Have you forgotten?' Conversion experiences in list worlds

### 2016-10-17 lists_conversion_experience.rmd
mainly playing with formatting

---
title: "An Example Using the Tufte Style"
author: "John Smith"
output:
  tufte::tufte_handout: default
tufte::tufte_html: default
---

@@

```{r setup, cache=FALSE, include=FALSE}
library(knitr)
output <- opts_knit$get("rmarkdown.pandoc.to")
opts_chunk$set(warnings=FALSE)
opts_chunk$set(messages=FALSE)
```

>>>>

---
title: "'Have you forgotten?' Conversion experiences in list worlds"
author: "Adrian Mackenzie"
output:
    tufte::tufte_handout: default
    tufte::tufte_html: default
---

@@

```{r setup, cache=FALSE, include=FALSE}
library(knitr)
output <- opts_knit$get("rmarkdown.pandoc.to")
opts_chunk$set(warning=FALSE)
opts_chunk$set(message=FALSE)
opts_chunk$set(error=TRUE)
```
